Interisland movements and oceanic swimming of woodland caribou in Newfoundland

### 2020-05-11 paper/manuscript.Rmd
question 1
question 2
question 3

>>>>

2) At which varying temporal and ecological scale do caribou choose to swim
between islands? Does the time of day, weather, seasonal trends, or availability
of food influence swimming?

3) Does reproductive status (presence of a calf-at-heel) or demographics (age,
sex) influence propensity for oceanic swimming? Our initial observation was of
an adult male, but the only collared individuals are adult females. Are younger
animals more likely to swim if they are outcompeted? More likely? Are males more
likely when in the summer their only concern is foraging, given the relatively
minimal predation risk they face without calves?
